%%	build-queue:
%%	
%%	¦¦¦ very first run. No .ist files yet
%%	¦¦	index, citation/bibliography or glossary changed
%%	¦	every change apart from the above mentioned. Double run for labels and toc.
%%	
%%	¦¦¦xelatex
%%	¦¦makeglossaries
%%	¦¦makeindex
%%	¦¦bibtex
%%	¦xelatex
%%	¦xelatex
%%	

\RequirePackage[l2tabu,orthodox]{nag}
\documentclass[10pt,a4paper,titlepage,twoside,english,final]{zhawreprt}

\include{packages}
\if false
\include{glossaryentries}
\fi

\include{zhawSetup}

\begin{document}

\maketitle

\chapter*{Abstract}\label{sec:Abstract}
\notes{\item Zusammenfassung}


\chapter*{Preface}\label{sec:Preface}
\notes{\item Stellt den persönlichen Bezug zur Arbeit dar und spricht Dank aus.}
The \gls{SSH} protocol \citep{rfc253,rfc6668,rfc8268,rfc8308,rfc8332} is a system that allows a user to log in on a remote machine and perform tasks on that remote machine via a \gls{CLI}. \gls{SSH} is widely known and used in everyday tasks. However: It is now over twelve years old in its current form. One of the problems with \gls{SSH} is its complexity, both in the initial phase when key material is exchanged, but also later, for example because the server must always decide whether to return a character that has been sent to it or not (echo).

The goal of this work is a radically simplified protocol, which in its functions is similar to \gls{SSH} (N.B. the similarity concerns the functions, not necessarily the protocol details). I develop the protocol, as well as a client and a server - all in \gls{Go}. I demonstrate that the software can replace \gls{SSH} by showing that it can handle several common use cases, among them:

\begin{itemize}
\item Interactive session
\item \texttt{Rsync} with my solution as transport protocol
\end{itemize}

This bachelor thesis was proposed by Dr. Stephan Neuhaus \citep{BA19_neut_03} and aroused my interest as it is a challenge in the domain of information security and will produce a palpable result.

On this note I would like to thank \gls{ZHAW} for granting me the opportunity to do my Bachelors thesis here and Dr. Stephan Neuhaus for helping me along the way of this Bachelors thesis.
\\\\
This thesis has been worded with technically literate readers in mind. However: For core concepts and special terms, a glossary can be found at \ref{sec:Glossary}.

\makedeclarationoforiginality

\tableofcontents

\chapter{Introduction}\label{chp:Introduction}
\section{Initial Position}\label{sec:InitialPosition}
\notes{
\item Nennt bestehende Arbeiten/Literatur zum Thema -> Literaturrecherche
\item Stand der Technik: Bisherige Lösungen des Problems und deren Grenzen
\item (Nennt kurz den Industriepartner und/oder weitere Kooperationspartner und dessen/deren Interesse am Thema Fragestellung)
}
There was no thesis done on this subject that could have been used as reference. There are however several software projects that deal with a similar problem.

\subsection{OpenSSH}\label{ssec:OpenSSH}
The most noteworthy work to mention is of course \gls{SSH} itself. \cite{openssh} is the name of the open source project which provides millions of administrators and developers with the ability to securely connect to a remote host. It replaces the up until then widely used protocols like \texttt{telnet}\ref{ssec:Telnet} and \texttt{rlogin}/\texttt{rsh}\ref{ssec:BerkeleyRCommands}.\\
\gls{SSH} uses \gls{TLS} to secure the communication channel between two peers and has earned itself a spot on the low end of the \gls{port} table: It occupies \gls{port} 22.\\
\gls{SSH}s features can be used very flexibly: After it builds up a secure connection between a client and a server, it can be used to remotely login and use a terminal on that machine.
It can also forward traffic on local ports to the remote host through the secure channel. This is also used by third party programs such as \texttt{rsync}.\\
When it comes to the log in procedure itself, \gls{SSH} allows for standard user log in using the \gls{API} of the \glspl{PAM}. Another feature is whitelisting of clients via their public keys, which barres intrusion via hijacked user-password-credentials.\\
After a secure connection could be established, there are multiple possibilities to use the opened channel. One is to forward the \gls{GUI} of a remote program to the client. Another one is to use this channel to tunnel more connections through it: For example can the traffic of an application which uses a specific \gls{port} be forwarded to the remote host. This can obscure and secure this traffic between the host and the server.

\subsection{Telnet}\label{ssec:Telnet}
Telnet\citep{rfc15,rfc854} is an old(1969) and deprecated communication protocol which doesn't feature any security. However, in other implementations, \gls{TELNETS} was proposed, which features encryption over the communication channel.\\
Telnet still has 23 as its very own \gls{port} assigned to it.
\subsubsection{Go-Telnet}
Go-Telnet\citep{gotelnet} is a \gls{TELNETS} supporting client-server-application which has been implemented in \gls{Go}.

\subsection{Berkeley r-commands}\label{ssec:BerkeleyRCommands}
The Berkley r-commands are a set of commands to do certain tasks on remote hosts. Those tasks are similar to their counterparts without a leading "\texttt{r}".
\begin{itemize}
\item \texttt{rlogin}\\
This command connects to the host and performs a \texttt{login} command, which includes authentication and if successful, spawning a user \gls{shell}.
\item \texttt{rsh}\\
\texttt{rsh} spawns a \gls{shell} without the log in process.
\item \texttt{rexec}\\
With this command, the user can log in to a remote machine and execute one command.
\item \texttt{rcp}\\
Using this command gives the user the ability to copy from and to a remote host.
\item \texttt{rwho}\\
This command tells the user what users are currently logged in on the remote machine.
\item \texttt{rstat}\\
\texttt{rstat} displays file system information from remote hosts.
\item \texttt{ruptime}\\
With this command, the user can see the uptime, number of logged in users and current work load of the remote machine.
\end{itemize}


\section{Task}\label{sec:Task}
\notes{
\item Formuliert das Ziel der Arbeit
\item Verweist auf die offizielle Aufgabenstellung des/der Dozierenden im Anhang
\item (Pflichtenheft, Spezifikation)
\item (Spezifiziert die Anforderungen an das Resultat der Arbeit)
\item (Übersicht über die Arbeit: stellt die folgenden Teile der Arbeit kurz vor)
\item (Angaben zum Zielpublikum: nennt das für die Arbeit vorausgesetzte Wissen)
\item (Terminologie: Definiert die in der Arbeit verwendeten Begriffe)
}
The objective of this thesis is to create a simplified communication protocol between a client and a server to allow the client to log in on the server.

\chapter{Theoretical Principles}\label{chp:TheoreticalPrinciples}


\chapter{Method}\label{chp:Method}
\notes{
\item (Beschreibt die Grundüberlegungen der realisierten Lösung (Konstruktion/Entwurf) und die Realisierung als Simulation, als Prototyp oder als Software-Komponente)
\item (Definiert Messgrössen, beschreibt Mess- oder Versuchsaufbau, beschreibt und dokumentiert Durchführung der Messungen/Versuche)
\item (Experimente)
\item (Lösungsweg)
\item (Modell)
\item (Tests und Validierung)
\item (Theoretische Herleitung der Lösung)
}

\chapter{Results}\label{chp:Results}
\notes{\item (Zusammenfassung der Resultate)}

\chapter{Discussion And Prospects}\label{chp:DiscussionAndProspects}
\notes{
\item Bespricht die erzielten Ergebnisse bezüglich ihrer Erwartbarkeit, Aussagekraft und Relevanz
\item Interpretation und Validierung der Resultate
\item Rückblick auf Aufgabenstellung, erreicht bzw. nicht erreicht
\item Legt dar, wie an die Resultate (konkret vom Industriepartner oder weiteren Forschungsarbeiten; allgemein) angeschlossen werden kann; legt dar, welche Chancen die Resultate bieten
}

\chapter{Index}\label{chp:Index}
\bibliography{reference}\label{sec:Bibliography}
\newpage
\printglossary\label{sec:Glossary}
\newpage
\listoffigures\label{sec:ListOfFigures}
\newpage
\listoftables\label{sec:ListOfTables}
\newpage
\lstlistoflistings\label{sec:ListOfListings}
\newpage
\printglossary[title=SymbolGlossary,type=symbols]\label{sec:SymbolGlossary}
\newpage
\printglossary[title=Acronym Glossary,type=\acronymtype]\label{sec:AcronymGlossary}
\newpage
\printindex\label{sec:Index}

\appendix
\chapter{Appendix}\label{chp:Appendix}
\section{Project Management}\label{sec:ProjectManagement}
\notes{
\item Offizielle Aufgabenstellung, Projektauftrag
\item (Zeitplan) 
\item (Besprechungsprotokolle oder Journals)
}
\section{Others}\label{sec:Others}
\notes{
\item CD mit dem vollständigen Bericht als pdf-File inklusive Film- und Fotomaterial
\item (Schaltpläne und Ablaufschemata)
\item (Spezifikationen u. Datenblätter der verwendeten Messgeräte und/oder Komponenten)
\item (Berechnungen, Messwerte, Simulationsresultate)
\item (Stoffdaten)
\item (Fehlerrechnungen mit Messunsicherheiten)
\item (Grafische Darstellungen, Fotos)
\item (Datenträger mit weiteren Daten(z. B. Software-Komponenten) inkl. Verzeichnis der auf diesem Datenträger abgelegten Dateien)
\item (Softwarecode)
}
\end{document}
